---
title: "Week 1 Assignment"
author: "Dave Froslie"
date: "September 11, 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1.0  Open R.  The first line of text in the console window tells you which version of R you are running (this should be version 3.1.2).  Copy this line of text into a document, to verify that you’ve installed the correct version.

R version 3.3.1 (2016-06-21) -- "Bug in Your Hair"
Copyright (C) 2016 The R Foundation for Statistical Computing
Platform: x86_64-w64-mingw32/x64 (64-bit)

Note that this is newer than 3.1.2.  Hopefully this won't be an issue for the class.

1.1 Calculate the cube root of 2015, as follows:
2015^(1/3)

```{r}
2015^(1/3)
```

1.2 Find the absolute value of 5.7 minus 6.8 divided by .58:
abs(5.7-6.8)/.58

```{r}
abs(5.7-6.8)/.58
```

1.3 Create a list of integers from 1 to 12 and call it “a”:
a = 1:12
a   #(this will print a, so you can paste it into your homework; do this each time)

```{r}
a = 1:12
a
```

1.4 Create a sequence of odd numbers from 1 to 11:
b = c(1, 3, 5, 7, 9, 11)
b

```{r}
b = c(1, 3, 5, 7, 9, 11)
b
```

1.5 Create the same sequence in another way:
c = seq(1,11, 2)
c

```{r}
c = seq(1,11, 2)
c
```

1.6 Take the natural log (ln) of a. (Note that this is done to the entire “vector” called a.)
ln.a = log(a)
ln.a

```{r}
ln.a = log(a)
ln.a
```

1.7 Compute the squares of the odd numbers from 1 to 11.

```{r}
b^2
```

1.8 Use ?sd to view the help file for the sd function.  What does it do?

sd computes the standard deviation of the values in x.

1.9. Create a variable Name that contains your first name.  Because your name is a character string, not a number, you will need to put it in quotes so that R knows not to go looking for a variable with that name:
Name = "Susan"
Then type
paste("My name is", Name)

```{r}
Name <- "Dave"
paste("My name is", Name)
```

1.10  When you shut down R, R will ask if you want to save the workspace image.  Always choose no. 
